\cvsection{Projects}
\begin{cventries}
  \cventry
    {UI Project for One Convergence's Client}
    {Virtual Infrastructure WebApp}
    {One Convergence, Hyderabad}
    {Nov. 2019 - PRESENT}
    {
      \begin{cvitems}
        \item {A Virtual Infrastructure based WebApp built with ReactJS and BackboneJS}
      \end{cvitems}
    }
  \cventry
    {Automation for One Convergence's Client}
    {Automation for UI/Windows/REST API}
    {One Convergence, Hyderabad}
    {Nov. 2018 - Oct. 2019}
    {
      \begin{cvitems}
        \item {Automation using python-selenium, python based propriety framework and Windows Powershell}
      \end{cvitems}
    }
  \cventry
    {UI Project for One Convergence}
    {Deep Learning WebApp}
    {One Convergence, Hyderabad}
    {Mar. 2018 - Nov. 2018}
    {
      \begin{cvitems}
        \item {A Deep Learning Platform for Data Scientists for running/managing datasets and models built with ReactJS}
      \end{cvitems}
    }
  \cventry
    {Self Indulged Project}
    {Artemis Cluster \href{https://hdesign.in/portfolio\#portfolio/All?code=ARTEMIS}{\textmd{\color{awesome-skyblue} [View]}}}
    {Private on Github}
    {Feb. 2019 - PRESENT}
    {
      \begin{cvitems}
        \item {A Dropbox Cluster Manager for deploying n-number of dropbox syncs in a linux based environment. Built using ReactJS, NodeJS, docker and REST API.}
      \end{cvitems}
    }
  \cventry
    {MCA Final Semester Project}
    {Automated Compute Infrastructure for Organizations using OpenStack}
    {}
    {Jan. 2018 - Jun. 2018}
    {
      \begin{cvitems}
        \item {A WebApp built on top of OpenStack using python and shell as a middleware. Built with PHP, JQuery and python-openstack-sdk}
      \end{cvitems}
    }
  \cventry
    {Self Indulged Project}
    {RASMUS \href{https://hdesign.in/portfolio\#portfolio/All?code=RASMUS}{\textmd{\color{awesome-skyblue} [View]}}}
    {Private on Github}
    {Aug. 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {A campus hiring management WebApp originally built for University of Hyderabad in 2017. Built with PHP, Ajax and JQuery}
      \end{cvitems}
    }
\end{cventries}
