\cvsection{Core Competencies}
% \cvproject{Technical}
\begin{itemize}
\item \textbf{UI Leadership:} Lead and mentor teams in the design and development of intuitive, responsive user interfaces across web platforms.
\item \textbf{UI/UX Design:} Expertise in Figma for creating wireframes, prototypes, and high-fidelity UI designs to deliver seamless, user-centered experiences.
\item \textbf{Full-Stack Development:} Proficient in ReactJS, Node.js, and microservices architecture to build scalable, high-performance applications end-to-end.
\item \textbf{Project Management:} Skilled in project planning, coordinating cross-functional teams, setting priorities, and ensuring timely delivery of high-quality products.
\item \textbf{Mentoring \& Team Development:} Actively mentor junior developers, providing guidance on best practices in UI/UX design, full-stack development, and team collaboration.
\item \textbf{Testing \& Automation:} Experienced in API integration, unit testing (Jest/Enzyme), and automation testing using tools like Selenium and Python.
% \item \textbf{Deployment \& Maintenance:} Hands-on experience deploying and managing web apps on AWS, Heroku, and shared hosting environments.
\end{itemize}

\cvsection{SKILLS}

\cvskill{Next.js/ReactJS, Node.js}{5}
\cvskill{SASS/LESS, PHP, Python}{5}
\cvskill{Generative AI, LangChain}{3}
\cvskill{Adobe XD, Figma}{4}
\cvskill{Jest/Enzyme, Selenium, Playwright}{4}
\cvskill{AWS, Docker, Shell Scripting}{5}

\cvsection{Certifications}
\smallskip
\begin{itemize}
\item \textbf{Hacker Rank - JavaScript} { • } \href{https://www.hackerrank.com/certificates/9e1b72fa37a2}{\textbf{Credentials}}
\item \textbf{Hacker Rank - React JS} { • } \href{https://www.hackerrank.com/certificates/6f620b44da51}{\textbf{Credentials}}
\item \textbf{AWS for Developers} { • } \href{https://www.dropbox.com/s/8a2mixx1nuaw0z9/CertificateOfCompletion_Learning%20Amazon%20Web%20Services%20AWS%20for%20Developers.pdf?dl=0}{\textbf{Credentials}}
\item \textbf{Kubernetes} { • } \href{https://www.dropbox.com/s/a0usxfusqvmeg82/CertificateOfCompletion_Learning%20Kubernetes.pdf?dl=0}{\textbf{Credentials}}
\item \textbf{UX Design with Adobe XD} { • } \href{https://www.udemy.com/certificate/UC-8155e0cf-c816-4172-9a82-1516f26752f1/}{\textbf{Credentials}}
\end{itemize}


\cvsection{Education}
\cvevent{Master of Computer Applications}{University of Hdyerabad}{ May 2015 -- May 2018}{}
%\divider
\cvevent{B.Sc Computer Science}{University of Delhi}{ May 2011 -- Mar 2014}{}
\divider

\smallskip
\begin{itemize}
% \item All India HCU MCA Entrance AIR 12
% \smallskip
\item Qualified UGC NET 2017
\smallskip
\item Secured 10 CGPA in MCA Final Project at SCIS, University of Hyderabad
\smallskip
\item Team Leader for Semi Finalist Team, Smart India Hackathon. Organized by Govt. of India
\smallskip
% \item Won several online and offline events at Annual Tech Fests organized by NIT Calicut and NIT Trichy in 2017
\end{itemize}


% \divider
% \cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}
