% Setting up the document with a modern, professional layout
\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{letterpaper, margin=0.5in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{helvet}

% Word wrap
\hyphenpenalty=10000
\tolerance=2000

% colors
\definecolor{darkteal}{RGB}{0, 96, 96}
\definecolor{linkblue}{RGB}{0, 102, 204}

% Description
\newcommand{\smallgray}[1]{\textcolor{darkgray!90}{\small #1}}

% Configuring fonts for a clean, professional look
\renewcommand{\familydefault}{\sfdefault}

% Customizing section headings for a modern style
\titleformat{\section}{\Large\bfseries\color{darkteal}}{}{0pt}{}
\titleformat{\subsection}{\normalsize\bfseries\color{black}}{}{0pt}{}
\titlespacing*{\section}{0pt}{16pt}{5pt}
\titlespacing*{\subsection}{0pt}{16pt}{4pt}

% Defining custom colors for hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue
}

% Setting up itemize environment for consistent formatting
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt}
\setlist[description]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt}

% Beginning the document
\begin{document}

% Header with personal information
\begin{center}
    {\LARGE\bfseries Himanshu Soni} \\
    \vspace{2pt}
    {\normalsize AI Project Lead | Development Team Lead | System Architecture} \\
    \vspace{2pt}
    Hyderabad, Telangana, India \\
    Phone: (+91)7382978592 | Email: \href{mailto:er.hsoni92@gmail.com}{er.hsoni92@gmail.com} \\
    Portfolio: \href{http://himanshusoni.dedyn.io}{himanshusoni.dedyn.io} | GitHub: \href{https://github.com/hsoni92}{github.com/hsoni92}
\end{center}

% Horizontal rule for separation
\hrulefill
\vspace{5pt}

% Professional Summary
\section{Professional Summary}
Results-driven AI Project Lead \& Development Team Lead with 7+ years of experience delivering end-to-end AI solutions from scoping to deployment. Proven expertise in AI project management, cloud-native architecture, and leading cross-functional teams. Spearheading AI-driven product initiatives, mentoring development teams, and delivering high-impact solutions. Known for translating business requirements into technical AI deliverables and accelerating AI feature delivery aligned with strategic goals.


% Professional Experience
\section{Professional Experience}
\textbf{AI Project Lead \& Development Team Lead} \\
\smallgray{One Convergence, Hyderabad | April 2025 -- Present}
\begin{itemize}
    \item Leading AI project initiatives from scoping to deliverables, managing cross-functional teams for cloud and AI platform development.
    \item Owning complete project lifecycle—from requirements gathering and technical scoping to development, testing, and production deployment.
    \item Mentored development teams on AI technologies, React.js best practices, and automated testing standards.
    \item Collaborated with product managers, AI researchers, backend, and DevOps teams to deliver seamless, scalable AI solutions.
    \item Championed UI migration from React.js to Next.js, improving performance and maintainability by 25\%.
\end{itemize}

\textbf{Senior Software Engineer} \\
\smallgray{One Convergence, Hyderabad | March 2021 -- March 2025}
\begin{itemize}
    \item Spearheaded UI development for DkubeX, enabling large-scale LLM deployment through intuitive interfaces.
    \item Built fast, responsive UIs using React.js, Node.js, and microservices to support real-time ML workflows.
    \item Developed and maintained automated test suites using Selenium and Python to ensure high reliability.
    \item Delivered 30+ product features through close collaboration with PMs and backend teams, with zero critical UI bugs.
\end{itemize}

\textbf{Software Engineer} \\
\smallgray{One Convergence, Hyderabad | August 2018 -- March 2021}
\begin{itemize}
    \item Developed feature-rich web applications with a focus on performance and usability using React.js and PHP.
    \item Automated UI and REST API testing using Python-Selenium, reducing QA cycles by 30\%.
    \item Contributed to cloud networking UI modules, integrating BackboneJS and Node.js to streamline user workflows.
\end{itemize}

\textbf{Web Developer (Freelance)} \\
March 2013 -- May 2018
\begin{itemize}
    \item Delivered custom web solutions using PHP, HTML/CSS for clients and college events at University of Delhi.
\end{itemize}

% break page
\newpage

% Key Projects
\section{Key Projects}
\textbf{TestHive - AI Education Platform} \\
\smallgray{Sole Developer | Independent Product Development | 2024 -- Present}
\begin{itemize}
    \item Architected and developed comprehensive AI-powered EdTech platform from concept to deployment, handling full-stack development, UI/UX design, and product strategy as sole developer.
    \item Built intelligent test generation system leveraging LangChain and Generative AI, implementing Revised Bloom Taxonomy \& NAAC guidelines for automated educational content creation and assessment.
    \item Delivered end-to-end product features including Google OAuth integration, AI-powered adaptive assessments, real-time analytics dashboard, and intelligent content generation with natural language processing.
    \item Designed responsive web application using Next.js and Node.js, implementing scalable microservices architecture with MongoDB for data persistence and Redis for session management.
    \item \smallgray{Read more: \href{https://www.himanshusoni.dedyn.io/work/testhive}{himanshusoni.dedyn.io/work/testhive}}
\end{itemize}

\textbf{Artemis - AI Cloud Data Platform - Independent Project} \\
\smallgray{AI-based SaaS for unified cloud storage search, automation, and cross-platform file operations | 2025 -- Present}
\begin{itemize}
    \item Leading AI project from conception to delivery, designing and building a web platform integrating Rclone with OAuth-enabled multi-cloud connectors (Google Drive, Dropbox, Koofr, etc.) for seamless file management.
    \item Scoped and architected LLM-driven natural language search and smart tagging based on metadata and content, enabling intelligent file discovery across providers.
    \item Delivered intelligent backup, sync, and automation workflows using Rclone bisync and shell-layer scripting for cross-cloud orchestration.
    \item Managed product UX design and developed the LLM query pipeline to enable dynamic, conversational multi-cloud operations.
    \item \smallgray{Read more: \href{https://www.himanshusoni.dedyn.io/work/artemis}{himanshusoni.dedyn.io/work/artemis}}
\end{itemize}

\textbf{DkubeX - Product Development} \\
\smallgray{AI platform for scalable deployment of open-source LLMs | February 2024 -- Present}
\begin{itemize}
    \item Led AI project scoping and translated 50+ user stories into intuitive, production-ready UX designs using Figma, improving feature discoverability and user flow.
    \item Managed AI project planning and estimation for multiple epics, streamlining frontend delivery timelines by up to 20\%.
    \item Delivered AI-driven UI features across 12+ release cycles, ensuring design consistency, responsiveness, and cross-browser compatibility.
\end{itemize}

\textbf{Azure Cluster Deployment Wizard - Product Development} \\
\smallgray{Visual tool for configuring, validating, and deploying clusters on Azure | February 2024 -- Present}
\begin{itemize}
    \item Led UI architecture using React, enabling graphical setup of cloud resources, network topologies, and deployment configurations.
    \item Built Node.js middleware to handle long-running workflows such as connectivity checks, environment validation, and provisioning.
    \item Integrated cloud APIs to support resource discovery and simulate network connectivity (ICMP, TCP, HTTP) prior to infrastructure rollout.
    \item Supported hybrid setups with high-availability options and permission-bound deployments across existing and new cloud infrastructure.
\end{itemize}

\textbf{Hybrid Multi-Cloud - UI Development} \\
\smallgray{Cloud networking interface for an enterprise hybrid cloud platform | 2019 -- Present}
\begin{itemize}
    \item Owned end-to-end UI development for 7 core networking modules including Subnets, VPN Gateway, VPN Connection, BGP Sessions, BGP Gateway, Advanced Network Controller, and Subnet Extension.
    \item Delivered features and resolved critical bugs across release cycles; led effort estimation and planning for assigned modules.
    \item Worked on a large-scale React codebase ensuring performance, accessibility, and seamless integration with backend APIs.
\end{itemize}

\textbf{Automated Compute Infrastructure for Organizations} \\
\smallgray{Self-service web platform for provisioning and managing compute resources using OpenStack | January 2019 -- October 2019}
\begin{itemize}
    \item Developed a full-stack web application using Python, PHP, and jQuery to automate infrastructure provisioning on OpenStack.
    \item Integrated \texttt{python-openstack-sdk} and Shell scripts to streamline middleware logic and ensure reliable orchestration of virtual resources.
\end{itemize}

% Core Competencies
\section{\\ Core Competencies}
\begin{itemize}
    \item \textbf{AI Project Leadership}: Leads end-to-end AI project scoping, development, and delivery for enterprise-grade applications.
    \item \textbf{AI \& Cloud Technologies}: Expert in Generative AI, LangChain, AWS, Docker, and open-source agentic AI stacks. Actively leading AI initiatives.
    \item \textbf{Project Management}: Skilled in coordinating cross-functional teams, sprint planning, and timely AI product delivery.
    \item \textbf{UI/UX Design}: Expert in Figma for wireframing, prototyping, and high-fidelity UI development for AI applications.
    \item \textbf{Full-Stack Development}: Develops robust AI applications using React.js, Next.js, Node.js, and microservices.
    \item \textbf{Testing \& Automation}: Implements unit tests (Jest, Enzyme) and automation frameworks (Selenium, Playwright) for AI systems.
\end{itemize}

% Skills
\section{Skills}
\begin{description}
    \item[AI Technologies:] Generative AI, LangChain, LangGraph (Agentic AI), Vector DB, OpenWeb UI, RAG Pipelines, MCP Servers
    \item[Frameworks/Libraries:] React.js, Next.js, Node.js
    \item[Languages:] JavaScript/Typescript, SASS/LESS, Python
    \item[Cloud/DevOps:] AWS, Docker, Kubernetes, Shell Scripting, OpenStack
    \item[Design Tools:] Figma, Photoshop, Illustrator
    \item[Testing Tools:] Jest, Enzyme, Selenium, Playwright
    \item[Other:] REST API, Microservices, Responsive Design, Agile Methodologies, Grafana, Loki, Promtail, Redis, MongoDB
\end{description}

% Certifications
\section{Certifications}
\begin{itemize}
    \item \href{https://www.dropbox.com/scl/fi/hf0k6cr86qwm2dbkb8iwb/CertificateOfCompletion_Learning-Amazon-Web-Services-AWS-for-Developers.pdf?rlkey=fo3zs0hayxttntiz3z2ax96y9&e=1&dl=0}{AWS for Developers} (2023)
    \item \href{https://www.credly.com/badges/fe8639a2-558c-45d8-8745-2f27a8415cb7/linked_in_profile}{Google -- Project Management Professional} (2025)
    \item \href{https://www.coursera.org/account/accomplishments/verify/A403DUFU26PH}{Google -- Prototyping with Figma} (2025)
\end{itemize}

% Education
\section{Education}
\textbf{Master of Computer Applications} \\
\smallgray{University of Hyderabad (May 2015 -- May 2018)}
\begin{itemize}
    \item Qualified UGC NET 2017
    \item Secured 10 CGPA in MCA Final Project at SCIS, University of Hyderabad
\end{itemize}
\textbf{B.Sc Computer Science} \\
\smallgray{University of Delhi (May 2011 -- March 2014)}

% Ending the document
\end{document}